---
title: "ADA Homework 1"
author: "Emily Raney"
date: "3/24/2021"
output: html_document
---
Challenge 1
```{r}
library(readr)
library(curl)
f <- curl("https://raw.githubusercontent.com/difiore/ada-2021-datasets/main/darwin.txt")
read.delim(f, header = FALSE, sep = "\n", col.names = FALSE)
oos_pgphs <- read_tsv("https://raw.githubusercontent.com/difiore/ada-2021-datasets/main/darwin.txt")
oos_pgphs
number_pgs <- nrow(oos_pgphs)
print(number_pgs)
```
Reading the data set as a tsv file yields a tibble with 56 rows. Each paragraph in the file is one row, so there are 56 chapters in the final chapter of On the Origin of Species, not including the title. 
```{r}
library(dplyr)
pgph_tf <- oos_pgphs[34, 1]
print(pgph_tf)
```
This prints paragraph 34, which starts with "The fact, as we have seen..."
```{r}
library(stringr)
split <- str_split(oos_pgphs, " ")
split
str(split)
```
There are 11,400 words in this vector
```{r}
sort(table(split), decreasing = TRUE) [1]
```
The most common word is 'the'; it appears 717 times
```{r}
df <- as.data.frame(split)
df
library(data.table)
oos_words <- table(split)
oos_words
once <- names(oos_words)[oos_words == 1]
once
```
There are 1576 words that appear only once
```{r}
five <- names(oos_words)[oos_words >= 5]
five
```
There are 333 words that appear at least five times
```{r}
final_quote <- oos_pgphs[56, 1]
final_quote
split_quote <- str_split(final_quote, " ")
split_quote
vect_fq <- unlist(split_quote)
vect_fq
third_el <- vect_fq[seq(3, length(vect_fq), 3)]
third_el
sort(third_el, decreasing = TRUE)
```
Challenge TWo
```{r}
t <- c(35, 88, 42, 84, 81, 30)
city <- c("Beijing", "Lagos", "Paris", "RioDeJaneiro", "SanJuan", "Toronto")
avg_high <- rbind(city, t)
avg_high
colnames(avg_high)
rownames(avg_high)
avg_high[1:6]
```
Temperatures of the first three cities on the list
```{r}
avg_high[c(5, 6, 9, 10)]
```
Temperatures of Paris and San Juan

Challenge 3
```{r}
m1 <- matrix(
  data = c(159:0), 
           nrow = 8, 
           ncol = 20,
  byrow = FALSE
)
m1
m1[5, 2]
m1[5:7, ]
m2 <- m1[3:6, 4:9]
m2
class(m2)
mode(m2)
```
The class of m2 is matrix, and the mode is numeric

Challenge 4
```{r}
a <- array(data = seq(from = 2, to = 800, by = 2), dim = c(5, 5, 4, 4))
a
a[1, 1, 1, 2]
a[2, 3, 2, ]
a[1:5, 1:5, 3, 3]
```
Challenge 5
```{r}
Superfamily_Lorisoidea <- c("Lorisidae", "Galagidae")
Superfamily_Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Superfamily_Tarsioidea <- c("Tarsiidae")
Superfamily_Ceboidea <- c("Cebidae", "Atelidae", "Pitheciidae")
Superfamily_Hominoidea <- c("Hylobatidae", "Hominidae")
Superfamily_Cercopithecoidea <- c("Cercopithecidae")
Infraorder_Lorisiformes <- list(Superfamily_Lorisoidea)
Infraorder_Lemuriformes <- list(Superfamily_Lemuroidea)
Infraorder_Tarsiiformes <- list(Superfamily_Tarsioidea)
Parvorder_Platyrrhini <- list(Superfamily_Ceboidea)
Parvorder_Catarrhini <- list(Superfamily_Hominoidea, Superfamily_Cercopithecoidea)
Infraorder_Simiiformes <-list(Parvorder_Platyrrhini, Parvorder_Catarrhini)
Suborder_Strepsirrhini <- list(Infraorder_Lorisiformes, Infraorder_Lemuriformes)
Suborder_Haplorrhini <- list(Infraorder_Tarsiiformes, Infraorder_Simiiformes)
Order_Primates <- list(Suborder_Strepsirrhini, Suborder_Haplorrhini)
str(Order_Primates)
Order_Primates
platyrrhines <- Order_Primates[[2]][[2]][[1]]
platyrrhines
class(platyrrhines)
```
The variable "platyrrhines" is a list
```{r}
tarsiers <- Order_Primates$Tarsiidae
tarsiers
```